---
title: "HW 2"
author: "309554005 黃睿宇"
CJKmainfont: 標楷體
output: 
  pdf_document:
    fig_caption: yes
    # keep_tex: yes
    includes:
      header-includes:
        -\usepackage{xeCJK}
    latex_engine: xelatex
  geometry: vmargin = 1
  linespread: 1.1
---

**Problem 1**

**(a)**
```{r}
pizza <- read.table(file="pizza2.txt", header=TRUE)
a <- pizza[pizza[,"heat"]=="Coal", "rating"]
sum(a) / length(a)
```
```{r}
summation  = 0
for (i in a){
  summation = summation + sum(i - mean(a))^2
}
(summation / (length(a)-1)) ^ 0.5

```
average rating of the pizzas baked by coal $= 4.688824\\$
standard deviation of the ratings baked by coal $= 0.4867479$\newline

```{r}
a <- pizza[pizza[,"heat"]=="Wood", "rating"]
sum(a) / length(a)
```
```{r}
summation  = 0
for (i in a){
  summation = summation + sum(i - mean(a))^2
}
(summation / (length(a)-1)) ^ 0.5

```
average rating of the pizzas baked by wood $= 3.8764\\$
standard deviation of the ratings baked by wood $= 1.537248$\newline

```{r}
a <- pizza[pizza[,"heat"]=="Gas", "rating"]
sum(a) / length(a)
```
```{r}
summation  = 0
for (i in a){
  summation = summation + sum(i - mean(a))^2
}
(summation / (length(a)-1)) ^ 0.5
```
average rating of the pizzas baked by gas $= 2.961013\\$
standard deviation of the ratings baked by gas $= 1.817251$\newline

<!-- 
```{r}
mean(pizza[pizza[,"heat"]=="Coal", "rating"])
sd(pizza[pizza[,"heat"]=="Coal", "rating"])
```
-->
The average rating of the pizzas baked by coal is the largest, and the rating is the most concentrated. On the contrary, the average rating of the pizzas baked by gas is the smallest, and the rating is the most dispersed.\newline\newline


**(b)**
```{r}
model <- lm(rating ~ heat, data=pizza)
anova(model)
```
Since $\text{p-value} = 8.184\times 10^{-5} < 0.05$, we could conclude that there is significant difference among variables in heat source. Through F value, we could also infer that the difference within each heat source might be larger than that among different heat sources.\newline\newline


**(c)**
```{r}
summary(model)
```
For coal: $\text{estimated coefficient} = 4.6888$, $\text{p-value} < 2\times 10^{-16}\\$
For gas: $\text{estimated coefficient} = -1.7278$, $\text{p-value} = 0.000109\\$
For wood: $\text{estimated coefficient} = -0.8124$, $\text{p-value} = 0.133289$\newline\newline


**(d)**\newline
In univariate analysis, we could only know the information of each variable. While in ANOVA, we could know whether the averages in different heat sources are equal or not. And from the result obtained in (a) is similar as (c), we could know that the variation of coal is the largest among the three.\newline\newline


**Problem 2**
```{r}
model1 <- lm(rating ~ heat + area + cost, data=pizza)
summary(model1)

model2 <- lm(rating ~ heat_re + area + cost, data=pizza)
summary(model2)
```
If we use "heat_re" as the predictor variables, it will have the weight error (the weight of gas is two times larger than that of wood).\newline

```{r}
model1 <- lm(rating ~ heat + area + cost, data=pizza)
predict(model1, data.frame(heat="Coal", area="LittleItaly", cost=2.5))

model2 <- lm(rating ~ heat_re + area + cost, data=pizza)
predict(model2, data.frame(heat_re=0, area="LittleItaly", cost=2.5))
```
prediction of model a $= 2.606232\\$
prediction of model b $= 2.776521$\newline\newline


**Problem 3**
```{r}
x1 <- pizza[pizza[,"area"]=="Chinatown", "rating"]
m1 <- mean(x1)
U1 <- m1 + qnorm(0.975) * sd(x1) / sqrt(length(x1))
L1 <- m1 - qnorm(0.975) * sd(x1) / sqrt(length(x1))

x2 <- pizza[pizza[,"area"]=="EVillage", "rating"]
m2 <- mean(x2)
U2 <- m2 + qnorm(0.975) * sd(x2) / sqrt(length(x2))
L2 <- m2 - qnorm(0.975) * sd(x2) / sqrt(length(x2))

x3 <- pizza[pizza[,"area"]=="LES", "rating"]
m3 <- mean(x3)
U3 <- m3 + qnorm(0.975) * sd(x3) / sqrt(length(x3))
L3 <- m3 - qnorm(0.975) * sd(x3) / sqrt(length(x3))

x4 <- pizza[pizza[,"area"]=="LittleItaly", "rating"]
m4 <- mean(x4)
U4 <- m4 + qnorm(0.975) * sd(x4) / sqrt(length(x4))
L4 <- m4 - qnorm(0.975) * sd(x4) / sqrt(length(x4))

x5 <- pizza[pizza[,"area"]=="SoHo", "rating"]
m5 <- mean(x5)
U5 <- m5 + qnorm(0.975) * sd(x5) / sqrt(length(x5))
L5 <- m5 - qnorm(0.975) * sd(x5) / sqrt(length(x5))

y <- c(m1, m2, m3, m4, m5)
U <- c(U1, U2, U3, U4, U5)
L <- c(L1, L2, L3, L4, L5)

require(plotrix)
plotCI(1:5, y, ui=U, li=L, xlab="index", ylab="area")
```
We could see that the largest mean rating is in EVillage, while its confidence interval is the smallest. The smallest mean rating is in Chinatown, while its confidence interval is the largest.