---
title: "HW 3"
author: "309554005 黃睿宇"
CJKmainfont: 標楷體
output: 
  pdf_document:
    fig_caption: yes
    # keep_tex: yes
    includes:
      header-includes:
        -\usepackage{xeCJK}
    latex_engine: xelatex
  geometry: vmargin = 1
  linespread: 1.1
---

**Problem 1**

**(a)**
```{r}
data1 <- read.csv(file="wastewater.csv", header=TRUE)
AF <- data1$AF
FS <- data1$FS
FCC <- data1$FCC
treatment <- c(AF, FS, FCC)
method <- c(rep("AF",10), rep("FS",10), rep("FCC",10))
model <- aov(treatment ~ method, data=data1)
summary(model)
```
Since $\text{p-value} = 1.03\times 10^{-10} < 0.05$, we could conclude that there is significant difference among three treatment methods.\newline\newline


**(b)**
```{r}
boxplot(treatment ~ method, data=data1)
```
Since the overall value of foam separation is larger than other groups, its removal ability should be the best.\newline\newline


**Problem 2**

```{r}
data2 <- read.csv(file="Fern.csv", header=TRUE)
growth <- data2$Response_area
block <- data2$Block_age
treatment <- data2$wave_light
model <- aov(growth ~ block+treatment, data=data2)
summary(model)
```

**(a)**\newline
Age is the blocking variable.\newline
Since $\text{p-value} = 0.0176 < 0.05$, we could conclude that the blocking effect (age) exists at 5% level of significance.\newline
```{r}
boxplot(growth ~ block, data=data2, main="Boxplot of growths and blocks")
```
We could get the same conclusion from the boxplot.\newline\newline


**(b)**\newline
Since $\text{p-value} = 0.2713 > 0.05$, we could conclude that the treatment effect (wavelength of light) does not exist at 5% level of significance.\newline
```{r}
boxplot(growth ~ treatment, data=data2, main="Boxplot of growths and treatments")
```
We could get the same conclusion from the boxplot.\newline\newline


**Problem 3**

**(a)**
```{r}
data3 <- read.csv(file="Cotinine.csv", header=TRUE)
cotinine <- data3$cotinine
gender <- as.factor(data3$Gender)
racial <- as.factor(data3$Race)

interaction.plot(x.factor = racial,     # variable to plot on x-axis
                 trace.factor = gender, # variable to specify "traces"; here, lines
                 response = cotinine,   # variable to plot on y-axis
                 fun = mean,            # summary statistic to be plotted for response variable
                 type = "b",            # type of plot, here "l" for lines
                 xlab = "Racial",
                 ylab = "Cotinine")
```
Since the two lines aren't parallel, we could infer that there exists interaction effect.\newline\newline


**(b)**
```{r}
data3 <- data.frame(cotinine, gender, racial)
model <- aov(cotinine ~ gender+racial+gender*racial, data=data3)
summary(model)
```
Since $\text{p-value} = 0.527 > 0.05$, we could conclude that the interaction effect does not exist at 5% level of significance.\newline\newline


**(c)**
```{r}
model <- aov(cotinine ~ gender+racial, data=data3)
summary(model)
```
For gender factor, since $\text{p-value} = 0.651 > 0.05$, we could conclude that the gender factor has no effect on the cotinine level.\newline
For racial factor, since $\text{p-value} = 0.156 > 0.05$, we could conclude that the racial factor has no effect on the cotinine level as well.\newline\newline

```{r}
model <- aov(cotinine ~ gender, data=data3[which(racial=="White"),])
summary(model)
```
Since $\text{p-value} = 0.496 > 0.05$, we could conclude that the white racial has no effect on the cotinine level.\newline
```{r}
model <- aov(cotinine ~ gender, data=data3[which(racial=="Black"),])
summary(model)
```
Since $\text{p-value} = 0.883 > 0.05$, we could conclude that the black racial has no effect on the cotinine level.